\section{Introduction}

\begin{frame}{Introduction to Inconsistent Information}
    \begin{itemize}
        \item \textbf{Knowledge Representation Challenge}
              \begin{itemize}
                  \item Handling inconsistent information is a fundamental challenge in knowledge representation and reasoning.
                  \item Inconsistencies can arise due to conflicting data, errors, or evolving knowledge.
              \end{itemize}
        \item \textbf{Classical Logic Limitations}
              \begin{itemize}
                  \item Classical logic deems any inconsistency as catastrophic, leading to \textbf{explosive} conclusions.
                  \item An inconsistent knowledge base is considered \textbf{useless} in classical semantics.
              \end{itemize}
        \item \textbf{Need for Alternative Approaches}
              \begin{itemize}
                  \item Not all inconsistencies have the same impact; some may be localized.
                  \item We require methods to handle and quantify inconsistencies without discarding the entire knowledge base.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Classical vs. Paraconsistent Logic}
    \begin{block}{Classical Logic}
        \begin{itemize}
            \item \textbf{Principle of Explosion}: From a contradiction, anything can be inferred (\( \forall \phi, \psi: \{\phi, \neg \phi\} \vdash \psi \)).
            \item Treats any inconsistency as catastrophic.
            \item Inconsistent knowledge bases are deemed invalid.
        \end{itemize}
    \end{block}
    \begin{block}{Paraconsistent Logic}
        \begin{itemize}
            \item Allows reasoning in the presence of contradictions.
            \item Two inconsistent knowledge bases can lead to different conclusions.
            \item Inconsistencies are localized, preventing the principle of explosion.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Inconsistency Measures}
    \begin{block}{Definition}
        An \darkhighlight{inconsistency measure} is a function \( \mathcal{I}(\mathcal{K}) \) that quantifies the extent and impact of inconsistencies within a knowledge base \( \mathcal{K} \).
    \end{block}
    \begin{itemize}
        \item \textbf{Purpose}:
              \begin{itemize}
                  \item Provides a quantitative metric rather than a binary consistent/inconsistent classification.
                  \item Helps in understanding the severity and localization of inconsistencies.
              \end{itemize}
        \item \textbf{Common Approach}:
              \begin{itemize}
                  \item Counting Minimal Inconsistent Subsets (MIS):
                        \[
                            \mathcal{I}_{\text{MI}}(\mathcal{K}) = \left| I_{\min}(\mathcal{K}) \right|
                        \]
                  \item \( I_{\min}(\mathcal{K}) \): Set of all minimal inconsistent subsets of \( \mathcal{K} \).
              \end{itemize}
        \item \textbf{Example}:
              \begin{itemize}
                  \item For \( \mathcal{K} = \{ a, \neg a, b \} \):
                  \item Minimal inconsistent subsets: \( I_{\min}(\mathcal{K}) = \{ \{ a, \neg a \} \} \)
                  \item Inconsistency measure: \( \mathcal{I}_{\text{MI}}(\mathcal{K}) = 1 \)
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Non-Monotonic Logics}
    \begin{block}{Definition}
        A \darkhighlight{non-monotonic logic} allows for the withdrawal of conclusions in the light of new, possibly conflicting, information.
    \end{block}
    \begin{itemize}
        \item \textbf{Contrast with Monotonic Logic}
              \begin{itemize}
                  \item In monotonic logic, adding new axioms cannot reduce the set of derivable conclusions.
                  \item Non-monotonic logic models the way human reasoning adapts to new information.
              \end{itemize}
        \item \textbf{Relevance to Inconsistency}
              \begin{itemize}
                  \item Non-monotonic logics can handle inconsistencies by revising conclusions.
                  \item They offer a framework for reasoning with incomplete or evolving knowledge.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Example: The Penguin Paradox}
    \begin{exampleblock}{Example: The Penguin Paradox}
        \begin{itemize}
            \item \textbf{Initial Knowledge Base}:
                  \begin{itemize}
                      \item All birds can fly.
                      \item Penguins are birds.
                  \end{itemize}
            \item \textbf{Inference}:
                  \begin{itemize}
                      \item Therefore, penguins can fly.
                  \end{itemize}
            \item \textbf{Adding New Information}:
                  \begin{itemize}
                      \item Penguins cannot fly.
                  \end{itemize}
            \item \textbf{Non-Monotonic Adjustment}:
                  \begin{itemize}
                      \item Previous conclusion is retracted.
                      \item Knowledge base accommodates the exception.
                  \end{itemize}
        \end{itemize}
    \end{exampleblock}
\end{frame}

\section{Answer Set Programming}

\begin{frame}{Answer Set Programming (ASP)}
    \begin{itemize}
        \item \textbf{Declarative Programming Paradigm}
              \begin{itemize}
                  \item ASP is a form of declarative programming focused on solving complex combinatorial problems.
                  \item It emphasizes \textbf{what} the problem is rather than \textbf{how} to solve it.
              \end{itemize}
        \item \textbf{Origins and Purpose}
              \begin{itemize}
                  \item Based on logic programming and non-monotonic reasoning.
                  \item Suitable for knowledge representation and reasoning tasks.
              \end{itemize}
        \item \textbf{Key Features}
              \begin{itemize}
                  \item Programs consist of rules with possible disjunctions in the head.
                  \item Incorporates two kinds of negation:
                        \begin{itemize}
                            \item \textbf{Strong Negation} ($\neg$): explicit denial of a fact.
                            \item \textbf{Default Negation} (\texttt{not}): assumption of falsehood in the absence of proof.
                        \end{itemize}
                  \item Solutions are expressed as \textbf{answer sets}, representing possible scenarios or models.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Syntax of Logic Programs}
    \begin{alertblock}{Rule Structure}
        A logic program \(P\) consists of rules of the form:
        \[
            \darkmathhighlight{l_0 \lor \dots \lor l_k} \leftarrow \yellowmathhighlight{l_{k+1}, \dots, l_m}, \mathhighlight{\text{not } l_{m+1}, \dots, \text{not } l_n}
        \]
        Where:
        \begin{itemize}
            \item \darkhighlight{Head}: \(head(r) = \{l_0, \dots, l_k\}\)
            \item \yellowhighlight{Positive Body}: \(pos(r) = \{l_{k+1}, \dots, l_m\}\)
            \item \highlight{Negative Body}: \(neg(r) = \{l_{m+1}, \dots, l_n\}\)
        \end{itemize}
    \end{alertblock}
    \begin{itemize}
        \item A \textbf{fact} is a rule with an empty body: \(head(r).\)
        \item A \textbf{constraint} is a rule with an empty head: \(\leftarrow body.\)
    \end{itemize}
\end{frame}

\begin{frame}{Semantics of Logic Programs}
    \begin{block}{Models and Answer Sets}
        \begin{itemize}
            \item A \textbf{model} \(M\) of a logic program \(P\) satisfies all rules in \(P\).
            \item \(M\) is a model if for every rule \(r\):
                  \begin{itemize}
                      \item If \(pos(r) \subseteq M\) and \(neg(r) \cap M = \emptyset\), then \(head(r) \cap M \neq \emptyset\).
                  \end{itemize}
            \item An \textbf{answer set} is a minimal model of \(P\).
        \end{itemize}
    \end{block}
    \begin{block}{Handling Negation}
        \begin{itemize}
            \item The presence of default negation (\texttt{not}) requires special treatment.
            \item Use the \textbf{Gelfond-Lifschitz reduct} to eliminate default negation when computing answer sets.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Reduct of a Logic Program}
    \begin{block}{Definition of Reduct}
        For a logic program \(P\) and a set of literals \(M\), the \darkhighlight{reduct} \(P^M\) is defined as:
        \[
            P^M = \{head(r) \leftarrow pos(r) \mid r \in P, \mathhighlight{neg(r) \cap M = \emptyset}\}
        \]
        \begin{itemize}
            \item All rules where the negative body is not contradicted by \(M\).
            \item Removes default negation to simplify the program.
        \end{itemize}
    \end{block}
    \begin{block}{Answer Sets via Reduct}
        A set \(M\) is an \darkhighlight{answer set} of \(P\) if \(M\) is a minimal model of the reduct \(P^M\).
    \end{block}
\end{frame}

\begin{frame}{Example: The Penguin Paradox in ASP}
    \begin{exampleblock}{Logic Program Encoding}
        \begin{itemize}
            \item \textbf{Facts}:
                  \[
                      \text{penguin(polly)}.
                  \]
            \item \textbf{Rules}:
                  \begin{align*}
                      \text{bird(X)}  & \leftarrow \text{penguin(X)}.                          \\
                      \text{flies(X)} & \leftarrow \text{bird(X)}, \ \text{not } \text{ab(X)}. \\
                      \text{ab(X)}    & \leftarrow \text{penguin(X)}.
                  \end{align*}
            \item \textbf{Interpretation}:
                  \begin{itemize}
                      \item Penguins are birds.
                      \item Birds typically fly unless they are abnormal (\texttt{ab(X)}).
                      \item Penguins are considered abnormal birds.
                  \end{itemize}
        \end{itemize}
    \end{exampleblock}
\end{frame}

\begin{frame}{Computing the Answer Set}
    \begin{block}{Candidate Answer Set \(M\)}
        \[
            M = \{\text{penguin(polly)},\ \text{bird(polly)},\ \text{ab(polly)}\}
        \]
    \end{block}
    \begin{block}{Constructing the Reduct \(P^M\)}
        \[
            P^M = \left\{
            \begin{array}{lcl}
                \text{penguin(polly)} &            &                       \\
                \text{bird(polly)}    & \leftarrow & \text{penguin(polly)} \\
                \text{ab(polly)}      & \leftarrow & \text{penguin(polly)}
            \end{array}
            \right\}
        \]
        \begin{itemize}
            \item The rule for \text{flies(polly)} is excluded since \(\text{not } \text{ab(polly)}\) is not satisfied.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Conclusion from the Example}
    \begin{itemize}
        \item In the reduct \(P^M\), \text{flies(polly)} cannot be derived.
        \item The candidate \(M\) is a minimal model of \(P^M\).
        \item Therefore, \(M\) is an \textbf{answer set} where \text{polly} does not fly.
        \item This illustrates how ASP handles exceptions and default reasoning.
    \end{itemize}
\end{frame}

\section{Strong Inconsistency}

\begin{frame}{Strong Inconsistency in Non-Monotonic Logics}
    \begin{itemize}
        \item \textbf{Non-Monotonic Logic Peculiarity}
              \begin{itemize}
                  \item Adding information can resolve inconsistencies.
                  \item Contrasts with monotonic logics, where adding information cannot restore consistency.
              \end{itemize}
        \item \textbf{Need for Refined Notions}
              \begin{itemize}
                  \item Traditional inconsistency concepts don't fully capture non-monotonic behavior.
                  \item Introduce \textbf{strong inconsistency} to better analyze inconsistencies.
              \end{itemize}
    \end{itemize}
    \begin{block}{Definition}
        A subset \( \mathcal{H} \subseteq \mathcal{K} \) is \darkhighlight{strongly \( \mathcal{K} \)-inconsistent} if all its supersets within \( \mathcal{K} \) are inconsistent.
    \end{block}
\end{frame}

\begin{frame}{Example and Importance of Strong Inconsistency}
    \begin{exampleblock}{Resolving Inconsistency}
        Knowledge Base \( \mathcal{K} = \{ b.,\ \neg b \leftarrow \text{not } a. \} \)
        \begin{itemize}
            \item \( \mathcal{K} \) is inconsistent since both \( b \) and \( \neg b \) can be derived.
            \item Adding \( a. \) resolves the inconsistency.
            \item Shows that some inconsistencies are not strong; they depend on missing information.
        \end{itemize}
    \end{exampleblock}
    \begin{itemize}
        \item \textbf{Importance of Strong Inconsistency}
              \begin{itemize}
                  \item Identifies conflicts that cannot be resolved by adding information.
                  \item Helps in developing inconsistency measures for non-monotonic logics.
              \end{itemize}
    \end{itemize}
\end{frame}

\section{Measures Based on Minimal Inconsistent Subsets}

\begin{frame}{Inconsistency Measures for Non-Monotonic Logics}
    \begin{itemize}
        \item \textbf{Extending Classical Measures}
              \begin{itemize}
                  \item Traditional measures count minimal inconsistent subsets (MIS).
                  \item Need to adapt these measures using strong inconsistency.
              \end{itemize}
        \item \textbf{Purpose of Measures}
              \begin{itemize}
                  \item Quantify the degree of inconsistency.
                  \item Provide insight into the severity and extent of conflicts.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Inconsistency Measures}
    \begin{block}{Measure \( \mathcal{I}_{\text{MSI}} \)}
        \[
            \mathcal{I}_{\text{MSI}}(\mathcal{K}) = \left| SI_{\min}(\mathcal{K}) \right|
        \]
        Counts the number of minimal strongly inconsistent subsets.
    \end{block}
    \begin{block}{Measure \( \mathcal{I}_{\text{MSI}^\text{C}} \)}
        \[
            \mathcal{I}_{\text{MSI}^\text{C}}(\mathcal{K}) = \sum\limits_{\mathcal{H} \in SI_{\min}(\mathcal{K})} \frac{1}{|\mathcal{H}|}
        \]
        Considers the size of each minimal strongly inconsistent subset.
    \end{block}
\end{frame}

\begin{frame}{Inconsistency Measures}
    \begin{block}{Measure \( \mathcal{I}_{\text{p}} \)}
        \[
            \mathcal{I}_{\text{p}}(\mathcal{K}) = \left| \bigcup\limits_{\mathcal{H} \in SI_{\min}(\mathcal{K})} \mathcal{H} \right|
        \]
        Counts the total number of problematic formulas involved.
    \end{block}
\end{frame}

\begin{frame}{Example: Calculating Inconsistency Measures}
    \begin{exampleblock}{Knowledge Base \( P \)}
        \[
            P = \left\{ \begin{array}{l}
                a \leftarrow \text{not } a,                  \\
                a \leftarrow \text{not } c,\ \text{not } d., \\
                b., c., d.
            \end{array} \right\}
        \]
    \end{exampleblock}
    \begin{itemize}
        \item \textbf{Minimal Strongly Inconsistent Subsets}:
              \[
                  SI_{\min}(P) = \left\{ \begin{array}{l}
                      \{ a \leftarrow \text{not } a,\ b.,\ c. \}, \\
                      \{ a \leftarrow \text{not } a,\ b.,\ d. \}
                  \end{array} \right\}
              \]
        \item \textbf{Calculations}:
              \begin{itemize}
                  \item \( \mathcal{I}_{\text{MSI}}(P) = 2 \)
                  \item \( \mathcal{I}_{\text{MSI}^\text{C}}(P) = \frac{1}{3} + \frac{1}{3} = \frac{2}{3} \)
                  \item \( \mathcal{I}_{\text{p}}(P) = 4 \)
              \end{itemize}
    \end{itemize}
\end{frame}

\section{Rationality Postulates}

\begin{frame}{Rationality Postulates}
    \begin{itemize}
        \item \textbf{Purpose}
              \begin{itemize}
                  \item Inconsistency measures quantify the \textbf{degree of inconsistency} in a knowledge base.
                  \item Not every function is suitable; we need criteria to ensure their \textbf{usefulness}.
                  \item These criteria are called \darkhighlight{rationality postulates}.
              \end{itemize}
        \item \textbf{Role in Inconsistency Measures}
              \begin{itemize}
                  \item Provide a foundation for \textbf{evaluating} and \textbf{comparing} inconsistency measures.
                  \item Ensure measures behave in a logically \textbf{consistent} and \textbf{expected} manner.
              \end{itemize}
    \end{itemize}
\end{frame}

\subsection{Basic Postulates}

\begin{frame}{Basic Rationality Postulates}
    \begin{block}{Consistency Postulate}
        For any knowledge base \( \mathcal{K} \):
        \[
            \mathcal{I}(\mathcal{K}) = 0 \quad \text{if and only if} \quad \mathcal{K} \text{ is consistent}
        \]
    \end{block}
    \begin{alertblock}{Monotonicity}
        For knowledge bases \( \mathcal{K} \) and \( \mathcal{K}' \):
        \[
            \mathcal{I}(\mathcal{K}) \leq \mathcal{I}(\mathcal{K} \cup \mathcal{K}')
        \]
    \end{alertblock}
    \begin{itemize}
        \item \textbf{Intuition}:
              \begin{itemize}
                  \item Adding information should not \textbf{decrease} inconsistency.
                  \item More information potentially introduces more \textbf{conflicts}.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Issue with Monotonicity in Non-Monotonic Logics}
    \begin{itemize}
        \item \textbf{Non-Monotonic Behavior}
              \begin{itemize}
                  \item In non-monotonic logics, \textbf{adding information can resolve inconsistencies}.
                  \item Thus, \( \mathcal{I}(\mathcal{K} \cup \mathcal{K}') \) may be \textbf{less} than \( \mathcal{I}(\mathcal{K}) \).
              \end{itemize}
        \item \textbf{Implications}
              \begin{itemize}
                  \item Classical monotonicity postulate may not hold.
                  \item Need to \textbf{revise} the monotonicity postulate for non-monotonic settings.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Example of Monotonicity Issue}
    \begin{exampleblock}{Example}
        Consider the logic program:
        \[
            P = \{a \lor b.,\ a \leftarrow b.,\ c \leftarrow \text{not }b.,\ \neg c \leftarrow \text{not }b.\}
        \]
        \begin{itemize}
            \item \(H = \{c \leftarrow \text{not }b.,\ \neg c \leftarrow \text{not }b.,\ a \leftarrow b.\} \in SI_{\min}(P)\)
            \item Adding \(P' = \{b.,\ d.,\ \neg d.\}\) resolves conflicts in \(P\).
            \item Now \(SI_{\min}(P \cup P') = \{\{d.,\ \neg d.\}\}\)
        \end{itemize}
    \end{exampleblock}
    \begin{alertblock}{Conclusion}
        \begin{itemize}
            \item Comparison of \(\mathcal{I}(P)\) and \(\mathcal{I}(P \cup P')\) becomes unreasonable.
        \end{itemize}
    \end{alertblock}
\end{frame}

\begin{frame}{Revising Monotonicity: Strong Monotonicity}
    \textbf{Definition}: \( \mathcal{K}' \) \highlight{preserves conflicts} of \( \mathcal{K} \) if:
    \[
        \forall \mathcal{H} \in SI(\mathcal{K}):\ \mathcal{H} \in SI(\mathcal{K} \cup \mathcal{K}')
    \]
    \begin{block}{Strong Monotonicity Postulate}
        If \( \mathcal{K}' \) preserves conflicts of \( \mathcal{K} \):
        \[
            \mathcal{I}(\mathcal{K}) \leq \mathcal{I}(\mathcal{K} \cup \mathcal{K}')
        \]
    \end{block}
    \begin{itemize}
        \item \textbf{Intuition}:
              \begin{itemize}
                  \item If new information doesn't \textbf{resolve} existing conflicts, inconsistency should not decrease.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Free Formulas}
    \begin{block}{Free Formulas}
        \textbf{Definition}: A formula \( \alpha \in \mathcal{K} \) is \highlight{free} if:
        \[
            \alpha \notin \bigcup\limits_{\mathcal{H} \in SI_{\min}(\mathcal{K})} \mathcal{H}
        \]
    \end{block}
    \begin{block}{SI-Free Postulate}
        If \( \alpha \) is free in \( \mathcal{K} \):
        \[
            \mathcal{I}(\mathcal{K}) = \mathcal{I}(\mathcal{K} \backslash \{\alpha\})
        \]
    \end{block}
\end{frame}

\begin{frame}{Issue with SI-Free}
    \begin{alertblock}{Problem}
        \begin{itemize}
            \item In non-monotonic logics, removing a free formula can affect \( SI_{\min}(\mathcal{K}) \).
            \item May introduce new conflicts or alter existing ones.
        \end{itemize}
    \end{alertblock}
    \begin{exampleblock}{Example}
        \begin{itemize}
            \item Consider \( P = \{ a \leftarrow \text{not } a,\ b.,\ c.,\ d. \} \)
            \item \( \alpha = d. \) is free in \( P \).
            \item Removing \( \alpha \) changes \( SI_{\min}(P) \).
        \end{itemize}
    \end{exampleblock}
\end{frame}

\begin{frame}{Independence Postulate with Neutral Formulas}
    \begin{block}{Neutral Formulas}
        \textbf{Definition}: A formula \( \alpha \) is \highlight{neutral} if:
        \[
            \forall \mathcal{H} \subseteq \mathcal{K}:\ \mathcal{H} \in C(\mathcal{K}) \Leftrightarrow \mathcal{H} \cup \{\alpha\} \in C(\mathcal{K})
        \]
    \end{block}
    \begin{block}{Independence Postulate}
        If \( \alpha \) is neutral in \( \mathcal{K} \):
        \[
            \mathcal{I}(\mathcal{K}) = \mathcal{I}(\mathcal{K} \backslash \{\alpha\})
        \]
    \end{block}
    \begin{itemize}
        \item \textbf{Benefit}:
              \begin{itemize}
                  \item Neutral formulas ensure that removing them doesn't affect inconsistency.
                  \item Addresses the issue with free formulas in non-monotonic settings.
              \end{itemize}
    \end{itemize}
\end{frame}

\subsection{Extended Postulates}

\begin{frame}{Extended Postulates: Syntax Sensitivity}
    \begin{itemize}
        \item \textbf{Issue with Syntax}
              \begin{itemize}
                  \item Inconsistency measures can be sensitive to the \textbf{syntax} of formulas.
                  \item Example: \( \{ a \land b \} \) vs. \( \{ a,\ b \} \)
              \end{itemize}
        \item \textbf{Adjunction Invariance}
              \begin{itemize}
                  \item An inconsistency measure should satisfy:
                        \[
                            \mathcal{I}(\mathcal{K} \cup \{ a \land b \}) = \mathcal{I}(\mathcal{K} \cup \{ a,\ b \})
                        \]
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Strong Equivalence Postulates}
    \begin{block}{Strong Equivalence}
        Knowledge bases \( \mathcal{K} \) and \( \mathcal{K}' \) are \highlight{strongly equivalent} if:
        \[
            \forall \mathcal{G}:\ \text{ACC}(\mathcal{K} \cup \mathcal{G}) = \text{ACC}(\mathcal{K}' \cup \mathcal{G})
        \]
    \end{block}
    \begin{block}{Strong Equivalence Postulate}
        If \( \mathcal{K} \equiv_S \mathcal{K}' \):
        \[
            \mathcal{I}(\mathcal{K}) = \mathcal{I}(\mathcal{K}')
        \]
    \end{block}
    \begin{itemize}
        \item \textbf{Implication}:
              \begin{itemize}
                  \item Inconsistency measure should be \textbf{invariant} under strong equivalence.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{FW-Strong Equivalence}
    \begin{block}{FW-Strong Equivalence}
        \(\mathcal{K}\) and \(\mathcal{K}'\) are \highlight{formula-wise strongly equivalent} if:
        \[
            \exists\ \rho : \mathcal{K} \rightarrow \mathcal{K}'\ \text{bijective},\ \text{such that}\ \{\alpha\} \equiv_S \{\rho(\alpha)\}\ \forall \alpha \in \mathcal{K}
        \]
    \end{block}
    \begin{block}{FW-Strong Equivalence Postulate}
        If \(\mathcal{K} \equiv_{\alpha} \mathcal{K}'\):
        \[
            \mathcal{I}(\mathcal{K}) = \mathcal{I}(\mathcal{K}')
        \]
    \end{block}
\end{frame}

\begin{frame}{Strong Equivalence Replacement}
    \begin{block}{Strong Equivalence Replacement}
        If \(\{\alpha\} \equiv_S \{\alpha'\}\) and \(\alpha,\ \alpha' \notin \mathcal{K}\):
        \[
            \mathcal{I}(\mathcal{K} \cup \{\alpha\}) = \mathcal{I}(\mathcal{K} \cup \{\alpha'\})
        \]
    \end{block}
    \begin{itemize}
        \item Inconsistency measure should be insensitive to replacement by strongly equivalent formulas.s
    \end{itemize}
\end{frame}

\begin{frame}{Separability and Strong Super-Additivity}
    \begin{block}{Separability}
        If:
        \begin{align*}
            SI_{\min}(\mathcal{K} \cup \mathcal{K}')            & = SI_{\min}(\mathcal{K}) \cup SI_{\min}(\mathcal{K}') \\
            SI_{\min}(\mathcal{K}) \cap SI_{\min}(\mathcal{K}') & = \emptyset
        \end{align*}
        Then:
        \[
            \mathcal{I}(\mathcal{K} \cup \mathcal{K}') = \mathcal{I}(\mathcal{K}) + \mathcal{I}(\mathcal{K}')
        \]
    \end{block}
    \begin{block}{Strong Super-Additivity}
        If \( \mathcal{K} \) and \( \mathcal{K}' \) \darkhighlight{preserve each other's conflicts} and \( \mathcal{K} \cap \mathcal{K}' = \emptyset \):
        \[
            \mathcal{I}(\mathcal{K}) + \mathcal{I}(\mathcal{K}') \leq \mathcal{I}(\mathcal{K} \cup \mathcal{K}')
        \]
    \end{block}
\end{frame}

\begin{frame}{Summary of Rationality Postulates}
    \begin{itemize}
        \item \textbf{Basic Postulates}:
              \begin{itemize}
                  \item \textbf{Consistency}
                  \item \textbf{Strong Monotonicity}
                  \item \textbf{SI-Free and Independence}
              \end{itemize}
        \item \textbf{Extended Postulates}:
              \begin{itemize}
                  \item \textbf{Equivalence Postulates} (Strong Equivalence, FW-Strong Equivalence, and Strong Equivalence Replacement)
                  \item \textbf{Separability}
                  \item \textbf{Strong Super-Additivity}
              \end{itemize}
        \item \textbf{Purpose}:
              \begin{itemize}
                  \item Ensure inconsistency measures are \textbf{robust}, \textbf{meaningful}, and logically \textbf{sound}.
                  \item Provide guidelines for developing and evaluating inconsistency measures in \textbf{non-monotonic logics}.
              \end{itemize}
    \end{itemize}
\end{frame}

\subsection{Compliance of Measures}

\begin{frame}{Compliance of Measures}
    \centering
    \begin{tabular}{lccc}
        \toprule
                                       & \(\mathcal{I}_{\text{MSI}}\) & \(\mathcal{I}_{\text{MSI}^\text{C}}\) & \(\mathcal{I}_{\text{p}}\) \\
        \midrule
        Consistency                    & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        Strong monotonicity            & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        SI-Free                        & \ding{55}                    & \ding{55}                             & \ding{55}                  \\
        Independence                   & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        Strong Equivalence             & \ding{55}                    & \ding{55}                             & \ding{55}                  \\
        FW-Strong Equivalence          & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        Strong Equivalence Replacement & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        Separability                   & \ding{51}                    & \ding{51}                             & \ding{55}                  \\
        Strong Super-Additivity        & \ding{51}                    & \ding{51}                             & \ding{51}                  \\
        \bottomrule
    \end{tabular}
\end{frame}

\begin{frame}{SI-Free Postulate}
    SI-free is not satisfied by any of the measures.
    \begin{exampleblock}{Example}
        Consider the logic program \(P = \{a \leftarrow \text{not } a, b., a \leftarrow \text{not }c, \text{not }d., b., c., d.\}\), which has:
        \[
            SI_{\min}(P) = \{\{a \leftarrow \text{not }a, b., b., c.\}, \{a \leftarrow \text{not }a, b., b., d.\}\}
        \]
        and \(\alpha = \{a \leftarrow \text{not }c, \text{not }d.\} \in Free_{\text{SI}}(P)\).

        The measures evaluate to:
        \[
            \mathcal{I}_{\text{MSI}}(P) = 2,\quad \mathcal{I}_{\text{MSI}^\text{C}}(P) = \frac{2}{3},\quad \mathcal{I}_{\text{p}}(P) = 4.
        \]
        But if \(\alpha\) is removed, they evaluate to:
        \[
            \mathcal{I}_{\text{MSI}}(P \backslash \{\alpha\}) = 1,\quad \mathcal{I}_{\text{MSI}^\text{C}}(P \backslash \{\alpha\}) = \frac{1}{2},\quad \mathcal{I}_{\text{p}}(P \backslash \{\alpha\}) = 2.
        \]
    \end{exampleblock}
\end{frame}

\section{Summary and Conclusion}

\begin{frame}{Summary}
    \begin{itemize}
        \item Addressed measuring inconsistencies in non-monotonic knowledge bases.
        \item Introduced strong inconsistency for non-monotonic logics.
        \item Applied strong inconsistency to extend inconsistency measures.
        \item Discussed rationality postulates for non-monotonic logics.
    \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
    \begin{itemize}
        \item Provided an overview of inconsistencies in non-monotonic logics.
        \item Future work: Improve measures and compliance with rationality postulates.
        \item Applications: Repairing knowledge bases by adding formulas.
    \end{itemize}
\end{frame}
